Volunteers in the Clouds: an Architecture for Low Cost and Potentially Massively Distributed Evolutionary Computation

### 2015-07-30 volunteer-clouds-ieee-ci-si.tex
Rearranging SoA by @fergunet and @mariosky

In the work presented in this paper, JavaScript was used in the full
stack, which has the advantage of using the same code for writing
desktop or command line and browser clients, both based in the EC
library NodEO \cite{DBLP:conf/gecco/GuervosVGES14}. This saves time when writing code and leverages
expertise acquired in the library itself. 
%The proposed software has the advantage of full stack JavaScript
%development..

@@

%FERGU: añadido el siguiente párrafo y referencia para justificar el uso de JS
Javascript is also compatible with the functional programming paradigm. According to 
\cite{swanresearch2015}, the benefits of using this kind of paradigm in 
metaheuristics optimization allows an improvement in communicability, 
reproducibility, interoperability, automated assembly, knowledge engineering 
and efficiency.

@@

As far as we know, this paper presents the only experiment that uses computational %FERGU: yo no estaría tan seguro de esto
resources that are as dissimilar as smartphones and powerful laptops
or desktop computers in a research center. The methodology used to
gather resources and the algorithms used will be described next, as
well as the results obtained with the setup.

@@

% Si te animas, propón un párrafo - JJ
% Ok, lo escribo. - Mario
% Voy escribiendo algo de HTML5 y Web Workers?, no necesariemente para esta sección.

>>>>

In the work presented in this paper, JavaScript was used in the full
stack, which has the advantage of using the same code for writing
desktop or command line and browser clients, both based in the EC
library NodEO \cite{DBLP:conf/gecco/GuervosVGES14}. This saves time when writing code and leverages
expertise acquired in the library itself. 
%The proposed software has the advantage of full stack JavaScript
%development..
%FERGU: añadido el siguiente párrafo y referencia para justificar el uso de JS
Javascript is also compatible with the functional programming paradigm. According to 
\cite{swanresearch2015}, the benefits of using this kind of paradigm in 
metaheuristics optimization allows an improvement in communicability, 
reproducibility, interoperability, automated assembly, knowledge engineering 
and efficiency.

@@

@@

As far as we know, this paper presents one of the few experiments that
uses computational 
%FERGU: yo no estaría tan seguro de esto
% Changed - JJ
resources that are as dissimilar as smartphones and powerful laptops
or desktop computers in a research center. The methodology used to
gather resources and the algorithms used will be described next, as
well as the results obtained with the setup.

@@

% Si te animas, propón un párrafo - JJ
% Ok, lo escribo. - Mario
% Voy escribiendo algo de HTML5 y Web Workers?, no necesariemente para
% esta sección. 
% Para la intro o esta sección - JJ
